Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-08-03 paper/paper.Rmd
corrected argument name theRange vs range

The "Spatial blocking" from package \pkg{blockCV} comes with various blocking options such as random (default) (`selection = "random"`), systematic (`selection = "systematic"`) or checkerboard pattern (`selection = "checkerboard"`).
Additionally, the user might supply a numeric value in meters via argument `theRange` (named just `range` in {mlr3spatiotempcv}) which will ensure a quadratic block pattern across the study area.
This kind of blocking might be of special interest for species distribution modeling as well as the possibility to supply a user-defined polygon via argument `rasterLayer` with predefined blocking zones.

@@

Alternatively, arguments `rows` and `cols` can be specified instead of `theRange`.
This allows to create rectangular blocks which honor the supplied `rows` and `cols` settings.

@@

<!-- spcv_block: how to set argument `theRange` -->
Method `"spcv_block"` requires the user to supply a value for argument `theRange` which denotes the block size used to create the blocking scheme across the study area.
This specification is non-trivial and therefore package \pkg{blockCV} provides some helper functions (`spatialAutoRange()` and `rangeExplorer()`) to conduct a data-driven estimation of the distance at which the spatial autocorrelation in the data levels off [@blockCV].
According to the package authors, this estimate should then be used for argument `theRange` to have a sensible value for the block sizes created in method `"spcv_block"`.
Rectangular partitioning can be problematic in irregularly shaped study areas where some of the resulting partitions may contain substantially fewer observations than others.

>>>>

The "Spatial blocking" from package \pkg{blockCV} comes with various blocking options such as random (default) (`selection = "random"`), systematic (`selection = "systematic"`) or checkerboard pattern (`selection = "checkerboard"`).
Additionally, the user might supply a numeric value in meters via argument `range` which will ensure a quadratic block pattern across the study area.
This kind of blocking might be of special interest for species distribution modeling as well as the possibility to supply a user-defined polygon via argument `rasterLayer` with predefined blocking zones.

@@

Alternatively, arguments `rows` and `cols` can be specified instead of `range`.
This allows to create rectangular blocks which honor the supplied `rows` and `cols` settings.

@@

<!-- spcv_block: how to set argument `theRange` -->
<!-- AB: argument is actually called range, not theRange -->
Method `"spcv_block"` requires the user to supply a value for argument `range` which denotes the block size used to create the blocking scheme across the study area.
This specification is non-trivial and therefore package \pkg{blockCV} provides some helper functions (`spatialAutoRange()` and `rangeExplorer()`) to conduct a data-driven estimation of the distance at which the spatial autocorrelation in the data levels off [@blockCV].
According to the package authors, this estimate should then be used for argument `range` to have a sensible value for the block sizes created in method `"spcv_block"`.
Rectangular partitioning can be problematic in irregularly shaped study areas where some of the resulting partitions may contain substantially fewer observations than others.
